The Emperor Has No Clothes

### 2011-04-01 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5809 ac11df5e-a788-c23b-a8e1-c758c323924d

\newcommand{\tpk}{$\tau_{\rm pk}$}
\newcommand{\mtpk}{\tau_{\rm pk}}
\newcommand{\mdv}{\delta v}
\newcommand{\ewabs}{$W_{\rm a}$}
\newcommand{\ewe}{$W_{\rm e}$}
\newcommand{\rtt}{$r_{\tau = 0.2}$}
\newcommand{\mrtt}{r_{\tau = 0.2}}
\newcommand{\bturb}{$b_{\rm turb}$}
\newcommand{\mbturb}{b_{\rm turb}}
\newcommand{\taud}{$\tau_{\rm dust}$}
\newcommand{\mtaud}{\tau_{\rm dust}}
\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgii}{\ion{Mg}{2}}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\feiis}{\ion{Fe}{2}$*$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {\, {\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

In the previous section, we demonstrated that the LBG clump model
of S+10 does not reproduce the observed \lya\ emission associated with
LBGs.   We also emphasize, however, that the radiative transfer of
\lya\ is sensitive to the intrinsic emission of the galaxy ($r \sim
10$\,kpc), the physics of the gas in the CGM ($r \sim 100$\,kpc), and
also the property of the IGM on larger scales ($r \sim 1-10$\,Mpc).
It is possible, therefore, that the observed \lya\ emission is
dominated by components other than a galactic-scale wind, indirectly
observed as blue-shifted absorption.  In this respect, the LBG clump
model cannot be ruled out.

>>>>

\newcommand{\mmc}{m_{\rm c}}
\newcommand{\tpk}{$\tau_{\rm pk}$}
\newcommand{\mtpk}{\tau_{\rm pk}}
\newcommand{\mdv}{\delta v}
\newcommand{\ewabs}{$W_{\rm a}$}
\newcommand{\ewe}{$W_{\rm e}$}
\newcommand{\rtt}{$r_{\tau = 0.2}$}
\newcommand{\mrtt}{r_{\tau = 0.2}}
\newcommand{\bturb}{$b_{\rm turb}$}
\newcommand{\mbturb}{b_{\rm turb}}
\newcommand{\taud}{$\tau_{\rm dust}$}
\newcommand{\mtaud}{\tau_{\rm dust}}
\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgii}{\ion{Mg}{2}}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\feiis}{\ion{Fe}{2}$*$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {\, {\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

@@

In the previous section, we demonstrated that the LBG clump model
of S+10 does not reproduce the observed \lya\ emission associated with
LBGs.   We also emphasize, however, that the radiative transfer of
\lya\ is sensitive to the intrinsic emission of the galaxy ($r \sim
10$\,kpc), the physics of the gas in the CGM ($r \sim 100$\,kpc), and
also the property of the IGM on larger scales ($r \sim 1-10$\,Mpc).
It is possible, therefore, that the observed \lya\ emission is
dominated by components other than a galactic-scale wind, indirectly
observed as blue-shifted absorption.  In this respect, the LBG clump
model cannot be ruled out by its discordance with the \lya\
observations.

In PKR11, we provided estimates for the energy and mass flux of the
LBG wind model, as approximated by a Sobolev solution.  We now
examine the same quantities for the clump model.  Consider a shell of
thickness $\Delta r$ at radius $r$ from an LBG galaxy.  We may relate
the number density of clumps $n(r)$ in this shell to the covering
fraction of the clumps $f_\rm{c}(r)$:

\begin{equation}
n(r) = \frac{f_{\rm c}(r)}{\sigma} \frac{1}{\Delta r}
\lable{eqn:density}
\end{equation}
with $\sigma$ the cross-section of the clump.  If each clump has a
mass $m_{\rm c}$ then the mass within the shell is

\begin{equation}
M_{\Delta r}(r) = 4\pi r^2 f_{\rm c}(r) \, \frac{m_{\rm c}}{\sigma}
\perd
\label{eqn:mshell}
\end{equation}
Following Sobolev formalism, we set the shell thickness with radius to
the velocity gradient of the flow

\begin{equation}
\Delta r = \Delta v_{\rm c} \ltp \frac{dv}{dr} \rtp^{-1}
\end{equation}
where $\Delta v_{\rm c}$ characterizes the velocity dispersion of the
clumps, from any combination of internal or external motions within
the shell.  In the following we adopt $\Delta v_{\rm c} = 10 \mkms$.

Lastly, we constrain the surface density of the clumps $m_{\rm
  c}/\sigma$ by demanding each clump be optically thick to the
metal-line transitions observed by S+10, e.g.\ \ion{Si}{2}~1526.  
This implies a minimum column density of Si$^+$ ions; we adopt
$\N{Si^+} > 10^{14} \cm{-2}$.  In turn, this implies a lower limit to
$m_{\rm c}/\sigma$.  For a solar abundance $n_{\rm H} = 10^{-4.5}
n_{\rm Si}$ and assuming no ionization correction, we find $N_{\rm H}
\ge 10^{18.5} \cm{-2}$ and therefore $m_{\rm c} / \sigma \ge 3.3
\sci{-2} \msun \, \rm pc^{-2}$ when one accounts for helium.

Adopting the minimum value for $\mmc/\sigma$,  we derive the mass,
mass flux, energy, and power profiles shown in
Figure~\ref{fig:mass_energy}.
[Note that the clump flux ($nvr^2$) is nearly constant (increases by a
factor of 2 somehow!) at $10^{-2}$ clumps/yr].
Regarding mass, we find the clump model has $M_{\rm TOT} \approx
10^{10} \msun$ [check] with nearly all of this matter existing at
radii $r>20$\,kpc.  Ironically, this material accounts for very little
of the down-the-barrel absorption\footnote{The only indisputable
  outflow component.} in the model: XX\%\ of the mass in the flow
corresponds to XX\%\ of the absorption.  
[Can momentum driven winds get this much energy/mass flux?]
We conclude that in their attempt to reconcile the absorption
transverse to LBGs with that along LBG sightlines that S+10 were
driven to this highly unrealistic scenario.

Both the energy and power of this outflow are predicted to achieve
very large quantities and, again, most of this occurs at large radii.
[Discuss \lya\ emission here]
